### 2021-01-19 README.Rmd
class output of fit function, convert predict to S3 method

```{r}
# Fit model
posterior_param_ex <- focal_vs_comp_ex %>%
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict_bayesian_model(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

>>>>

```{r}
# Fit model
posterior_param_ex <- focal_vs_comp_ex %>%
  fe_bayes_lm(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))
